### 2015-05-15 corral.tex
Cut to the chase in the abstract.
fix

\noindent\textbf{Race-Checking Instrumentation }
%
To detect data races with \corral, \whoop outputs a Boogie program instrumented with a simple, but effective encoding of race checks. Whenever there is a write access to a shared variable $s$, \whoop instruments the program as follows:
%
\begin{boogie}
s = e;         // original write
yield;         // allow for a context-switch
assert s == e; // check written value
\end{boogie}
%
Likewise, whenever there is a read access to $s$, \whoop instruments the program as follows:
%
\begin{boogie}
x = s;         // original read
yield;         // allow for a context-switch
assert x == s; // check read value
\end{boogie}
%
A \texttt{yield} statement denotes a nondeterministic context-switch, and is used by \corral to guide the sequentialization.

@@

\noindent\textbf{Sound Partial-Order Reduction }
%
By default, and assuming no race-freedom guarantees, \whoop instruments a \texttt{yield} after each shared memory access of each entry point, and after every lock and unlock operation.\footnote{We acknowledge that in the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} \whoop then sends this instrumented program to \corral, which leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: if, thanks to \whoop's analysis, we know that a given statement that accesses shared memory cannot be involved in a data race, we do not instrument a \texttt{yield} after this statement.  This is a form of \emph{partial order reduction}~\cite{DBLP:books/sp/Godefroid96}, and reduces the number of context-switches that \corral must consider in a \emph{sound} manner: there is no impact on the bugs that will be detected.  This is because each access, for which a \texttt{yield} is suppressed, is guaranteed to be protected by some lock (a consequence of lockset analysis).  If the access is a write, its effects are not visible by the other entry point in the pair until the lock is released.  If the access is a read, the value of the shared location cannot change until the lock is released.  The fact that a \texttt{yield} is placed after each unlock operation suffices to take account of communication between entry points via the shared memory location.

>>>>

\noindent\textbf{Race-Checking Instrumentation }
%
To detect data races with \corral, \whoop outputs a Boogie program instrumented with a simple, but effective encoding of race checks. Whenever there is a write access to a shared variable $s$, \whoop instruments the program as follows:
%
\begin{boogie}
s = e;         // original write
yield;         // allow for a context-switch
assert s == e; // check written value
\end{boogie}\vspace{-2mm}
%
Likewise, whenever there is a read access to $s$, \whoop instruments the program as follows:
%
\begin{boogie}
x = s;         // original read
yield;         // allow for a context-switch
assert x == s; // check read value
\end{boogie}\vspace{-2mm}
%
A \texttt{yield} statement denotes a nondeterministic context-switch, and is used by \corral to guide the sequentialization.

@@

\noindent\textbf{Sound Partial-Order Reduction }
%
By default, and assuming no race-freedom guarantees, \whoop instruments a \texttt{yield} after each shared memory access of each entry point, and after every lock and unlock operation.\footnote{We acknowledge that in the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} \whoop then sends this instrumented program to \corral, which leverages sequentialization to explore all possible thread interleavings up to a pre-defined bound. Our approach to accelerating \corral is simple and yet effective: if, thanks to \whoop's analysis, we know that a given statement that accesses shared memory cannot be involved in a data race, then we do not instrument a \texttt{yield} after this statement.  This is a form of \emph{partial order reduction}~\cite{DBLP:books/sp/Godefroid96}, and reduces the number of context-switches that \corral must consider in a \emph{sound} manner: there is no impact on the bugs that will be detected.  This is because each access, for which a \texttt{yield} is suppressed, is guaranteed to be protected by some lock (a consequence of lockset analysis).  If the access is a write, its effects are not visible by the other entry point in the pair until the lock is released.  If the access is a read, the value of the shared location cannot change until the lock is released.  The fact that a \texttt{yield} is placed after each unlock operation suffices to take account of communication between entry points via the shared memory location.
